\chapter{Personal Reports}

\section{Miles Strässle}
\subsection{What Went Well}
The project's success was marked by our resilience in solving numerous challenges along the way. We maintained the original architecture with only minor modifications, which proved to be effective.

\subsection{Areas for Improvement}
As this was our first project of this kind, we encountered some learning curves. In hindsight, a more thorough evaluation of technologies, particularly concerning DNS issues with ejabberd, would have been beneficial.

\subsection{Personal Highlights}
My personal journey through this project was enriching, especially in learning about Tor's onion routing, XMPP details, modern encryption, and developing a protocol within a complex architecture. The most rewarding moment was when the project come to function as intended.



\section{Svenja Sutter}
\subsection{What Went Well}
The final version of our chat application consists of multiple layers of security, effectively achieving our primary goal of implementing Post-Quantum Cryptography (PQC) encryption. This achievement is particularly significant given the flexible design of the wrapper, which allows for easy replacement with alternative PQC algorithms once the NIST Round 4 evaluations have been completed. Despite the complexity of multiple encryption and decryption processes, the chat application maintains good performance.

\subsection{Areas for Improvement}
The DNS routing issue proved to be a significant and time-consuming challenge. In retrospect, an evaluation of this aspect prior to implementation could have improved the process. In addition, the planning phase of the project lacked comprehensive detail. A more detailed plan would have provided a clearer overview and potentially streamlined the project's progress.

\subsection{Personal Highlights}
This project was my first experience with these technologies and it was both interesting and very educational. In addition, the immersion in post-quantum cryptography was particularly enjoyable. It provided valuable insights and a deeper understanding of this innovative field.
