\chapter{Introduction}
% Problem
In today's digital world, where privacy and data security are major concerns, we often compromise our personal information for convenience. Take WhatsApp as an example, in order to use it, we have to accept terms and conditions that allow for extensive data collection.\\ \\
% Ziel
We believe that control over personal information and private communications should be in our own hands, not stored on distant servers. That's why we are developing a peer to peer chat application as our semester assignment at the OST. Our app, qChat, prioritises privacy, so it doesn't store messages on external servers and ensures that your conversations remain confidential. Moreover, we are integrating the cutting-edge technology post-quantum cryptography. This advanced security feature is designed to protect your chats even against future threats like quantum computers. Our goal is to provide a way for people to chat without worry about their privacy.\\ \\
% Methode
To achieve our goals, we will evaluate and experiment with different technologies and learn about post-quantum technology and how to integrate an existing algorithm into our chat application. We plan to develop several prototypes: one dedicated to peer-to-peer (P2P) chat functionality, a proof of concept for post-quantum cryptography (PQC) encryption, and another for a basic frontend interface. Ultimately, we aim to integrate these components into a cohesive application.\\ \\
% Überblick der Arbeit
In this documentation, we will first examine various state-of-the-art technologies. We will then define and evaluate our requirements and then present an overview of the chat application, focusing on its architecture and security layers. Finally, we will perform an evaluation to assess the effectiveness and security of our chat application.
