\chapter*{Abstract}
\begin{itemize}
	\item \textbf{Introduction}:
	      Our application, qChat, is a decentralized, peer-to-peer (P2P) chat application meant for future-proof privacy. It uses the latest encryption algorithms to ensure secret message exchange in the post-quantum era.

	\item \textbf{Problem Addressed}: qChat addresses the growing concern for digital privacy and security, particularly in the face of quantum computing's potential to break current encryption standards.

	      Quantum computing poses a significant threat to current encryption methods, particularly due to advancements like Shor's Algorithm. This algorithm, in theory, allows quantum computers to break widelyused encryption schemes such as RSA and ECC much faster than conventional computers.

	\item \textbf{Result}:
	      The solution involves developing a peer-to-peer chat application using post-quantum cryptography (PQC), eliminating reliance on external servers for data storage. The project has successfully created a prototype demonstrating peer-to-peer functionality with integrated post-quantum cryptography.

	\item \textbf{Conclusion}:
	      These developments are significant as they provide a practical approach to secure communication, setting a precedent in the field of quantum-resistant digital communication.

	\item \textbf{Key Results}: The project has successfully created prototypes demonstrating P2P functionality, integrated PQC, and developed a user interface.

	\item \textbf{Evaluation of Results}: These developments are significant as they provide a practical approach to secure communication, setting a precedent in the field of quantum-resistant digital communication.

	\item \textbf{Future Implications}: The insights and technologies developed in qChat lay the groundwork for future advancements in secure communications. This also marks a significant advancement in protecting the private sphere in an increasingly interconnected post-quantum world.

\end{itemize}


